Decentralized autonomous organization to automate governance\\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-04-15 paper/Paper.tex
Changed to American style punctiation

We first describe a DAO's formation and basic functionality. We then discuss minority owner rights and propose a solution to the ``Majority Robbing the Minority Attack'' problem, the ``DAO split''. We then explore the smart contract code in detail, and conclude with an explanation and detailed specification of the ``DAO split''.

@@

In order to prevent ``proposal spam'', a minimal deposit can be required to be paid when creating a proposal, which gets refunded if quorum is achieved. If quorum is not achieved, the DAO keeps the proposal deposit. The value of the proposal deposit can be changed from the default value by the DAO through another proposal.

@@

There is a special function which is called the constructor. It has the same name as the contract ``DAO''. This function is only executed once, when the DAO is created.
In the DAO constructor, the following variables are set:
\begin{itemize}
 \item \verb|curator|
 \item \verb|daoCreator|
 \item \verb|proposalDeposit|
 \item \verb|rewardAccount|
 \item \verb|DAOrewardAccount|
 \item \verb|minValue|
 \item \verb|closingTime|
 \item \verb|privateSale|
 \item \verb|lastTimeMinQuorumMet|
 \item \verb|minQuorumDivisor|
 \item \verb|allowedRecipients|
\end{itemize}

>>>>

We first describe a DAO's formation and basic functionality. We then discuss minority owner rights and propose a solution to the ``Majority Robbing the Minority Attack'' problem, the ``DAO split.'' We then explore the smart contract code in detail, and conclude with an explanation and detailed specification of the ``DAO split.''

@@

In order to prevent ``proposal spam,'' a minimal deposit can be required to be paid when creating a proposal, which gets refunded if quorum is achieved. If quorum is not achieved, the DAO keeps the proposal deposit. The value of the proposal deposit can be changed from the default value by the DAO through another proposal.

@@

There is a special function which is called the constructor. It has the same name as the contract ``DAO.'' This function is only executed once, when the DAO is created.
In the DAO constructor, the following variables are set:
\begin{itemize}
 \item \verb|curator|
 \item \verb|daoCreator|
 \item \verb|proposalDeposit|
 \item \verb|rewardAccount|
 \item \verb|DAOrewardAccount|
 \item \verb|minValue|
 \item \verb|closingTime|
 \item \verb|privateSale|
 \item \verb|lastTimeMinQuorumMet|
 \item \verb|minQuorumDivisor|
 \item \verb|allowedRecipients|
\end{itemize}
